working title Compatibility system and stigma size are the main predictors of heterospecific pollen effect

### 2019-02-22 Manuscript_draft/Manuscript_draft.Rmd
some edits intro

For the understanding at what level or intensity the interference of pollen can occur is important to consider the relatedness of the interacting species. Closely related species are more likely to have similar traits @letten2015. The similarity in traits between closely related species can lead to higher chances of ovule usurpation/abortion @arceo2011 and therefore studies predict and show a greater negative effect of closely related species @ashman2013; @arceo2016. Few studies however, have focused on the impacts of heterospecific pollen on fitness of distantly related species @galen1989; @neiland1999. Despite the fact that far related species are also able to decrease species fitness (REFS). Yet, most insects and most stigmas have been found to carry multiple species of foreign pollen with little attention to degree of relatedness (Arceo-Gómez and Ashman (2016); Fang and Huang (2013). Understanding the role of foreign pollen from distantly related species thus deserves greater attention. The relatedness of foreign pollen gives a first snapshoot of where the pollen competition can occur and therefore could be a proxy of effect. With that said, @arceo2016 is the only work which has proven a greater effect of close related species through a meta-analysis with low sample sizes and lack of significance. Therefore, there is a need to study the effect of heterospecific pollen of far and close related species at community level beyond single pairwise interactions.

Heterospecific pollen studies in nature have the complexity added of great environmental variability which can lead to confounding interpretations. Moreover, the great diversity of floral structures and small sizes of some of them such as Asteraceae species make tedious or almost impossible the studies of heterospecific pollen on the field. For this reason, we investigated how floral reproductive traits and relatedness mediate the impact of heterospecific by creating an artificial co-flowering community in a glasshouse with 10 species belonging to three different families with different traits. Our study tries to answer the following question: To what extent do (i) floral reproductive traits and (ii) relatedness, mediate the impacts of heterospecific pollen on seed set.

>>>>

For the understanding at what level or intensity the interference of pollen can occur is important to consider the relatedness of the interacting species. Closely related species are more likely to have similar traits @letten2015. The similarity in traits between closely related species can lead to higher chances of ovule usurpation/abortion @arceo2011 and therefore studies predict and show a greater negative effect of closely related species @ashman2013; @arceo2016. Few studies however, have focused on the impacts of heterospecific pollen on fitness of distantly related species @galen1989; @neiland1999. Despite the fact that far related species are also able to decrease species fitness (REFS). Yet, most insects and most stigmas have been found to carry multiple species of foreign pollen with little attention to degree of relatedness (Arceo-Gómez and Ashman (2016); Fang and Huang (2013). Understanding the role of foreign pollen from distantly related species thus deserves greater attention. The relatedness of foreign pollen gives a first snapshoot of where the pollen competition can occur and therefore could be a proxy of effect. With that said, @arceo2016 is the only work which has proven a greater effect of close related species through a meta-analysis but with low sample sizes and lack of significance. Therefore, there is a need to study the effect of heterospecific pollen of far and close related species at community level beyond single pairwise interactions.

Heterospecific pollen studies in nature have the complexity added of great environmental variability which can lead to confounding interpretations. Moreover, the great diversity of floral structures and small sizes of some of them such as Asteraceae species make tedious or almost impossible the studies of heterospecific pollen on the field. For this reason, we investigated how floral reproductive traits and relatedness mediate the impact of heterospecific pollen by creating an artificial co-flowering community in a glasshouse with 10 species belonging to three different families with different traits. Our study tries to answer the following question: To what extent do (i) floral reproductive traits and (ii) relatedness, mediate the impacts of heterospecific pollen on seed set.

### 2019-02-22 Manuscript_draft/Manuscript_draft.tex
some edits intro

For the understanding at what level or intensity the interference of
pollen can occur is important to consider the relatedness of the
interacting species. Closely related species are more likely to have
similar traits Letten and Cornwell (2015). The similarity in traits
between closely related species can lead to higher chances of ovule
usurpation/abortion Arceo-Gómez and Ashman (2011) and therefore studies
predict and show a greater negative effect of closely related species
Ashman and Arceo-Gómez (2013); Arceo-Gómez and Ashman (2016). Few
studies however, have focused on the impacts of heterospecific pollen on
fitness of distantly related species Galen and Gregory (1989); Neiland
and Wilcock (1999). Despite the fact that far related species are also
able to decrease species fitness (REFS). Yet, most insects and most
stigmas have been found to carry multiple species of foreign pollen with
little attention to degree of relatedness (Arceo-Gómez and Ashman
(2016); Fang and Huang (2013). Understanding the role of foreign pollen
from distantly related species thus deserves greater attention. The
relatedness of foreign pollen gives a first snapshoot of where the
pollen competition can occur and therefore could be a proxy of effect.
With that said, Arceo-Gómez and Ashman (2016) is the only work which has
proven a greater effect of close related species through a meta-analysis
with low sample sizes and lack of significance. Therefore, there is a
need to study the effect of heterospecific pollen of far and close
related species at community level beyond single pairwise interactions.

Heterospecific pollen studies in nature have the complexity added of
great environmental variability which can lead to confounding
interpretations. Moreover, the great diversity of floral structures and
small sizes of some of them such as Asteraceae species make tedious or
almost impossible the studies of heterospecific pollen on the field. For
this reason, we investigated how floral reproductive traits and
relatedness mediate the impact of heterospecific by creating an
artificial co-flowering community in a glasshouse with 10 species
belonging to three different families with different traits. Our study
tries to answer the following question: To what extent do (i) floral
reproductive traits and (ii) relatedness, mediate the impacts of
heterospecific pollen on seed set.

>>>>

For the understanding at what level or intensity the interference of
pollen can occur is important to consider the relatedness of the
interacting species. Closely related species are more likely to have
similar traits Letten and Cornwell (2015). The similarity in traits
between closely related species can lead to higher chances of ovule
usurpation/abortion Arceo-Gómez and Ashman (2011) and therefore studies
predict and show a greater negative effect of closely related species
Ashman and Arceo-Gómez (2013); Arceo-Gómez and Ashman (2016). Few
studies however, have focused on the impacts of heterospecific pollen on
fitness of distantly related species Galen and Gregory (1989); Neiland
and Wilcock (1999). Despite the fact that far related species are also
able to decrease species fitness (REFS). Yet, most insects and most
stigmas have been found to carry multiple species of foreign pollen with
little attention to degree of relatedness (Arceo-Gómez and Ashman
(2016); Fang and Huang (2013). Understanding the role of foreign pollen
from distantly related species thus deserves greater attention. The
relatedness of foreign pollen gives a first snapshoot of where the
pollen competition can occur and therefore could be a proxy of effect.
With that said, Arceo-Gómez and Ashman (2016) is the only work which has
proven a greater effect of close related species through a meta-analysis
but with low sample sizes and lack of significance. Therefore, there is
a need to study the effect of heterospecific pollen of far and close
related species at community level beyond single pairwise interactions.

Heterospecific pollen studies in nature have the complexity added of
great environmental variability which can lead to confounding
interpretations. Moreover, the great diversity of floral structures and
small sizes of some of them such as Asteraceae species make tedious or
almost impossible the studies of heterospecific pollen on the field. For
this reason, we investigated how floral reproductive traits and
relatedness mediate the impact of heterospecific pollen by creating an
artificial co-flowering community in a glasshouse with 10 species
belonging to three different families with different traits. Our study
tries to answer the following question: To what extent do (i) floral
reproductive traits and (ii) relatedness, mediate the impacts of
heterospecific pollen on seed set.
